Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-05-14 markdown/kmorris_thesis.Rmd
Add matching for high intensity of lost voters Add city council competitiveness to matching

To test whether neighborhoods with lost voters had systematically lower turnout rates than similar neighborhoods without such disqualifications, I begin by using a matching model. Neighborhoods (defined as census tracts and block groups) are considered treated if they were home to *at least one* lost voter in the 2017 election; they are untreated if no residents were disqualified from the election because of a felony conviction. I use a genetic match to match treated to untreated census tracts and block groups. I match on a series of demographic and political indicators: racial characteristics, median income, education, age, population, share noncitizen,^[The Census Bureau does not make noncitizen estimates available at the block group level. As such, block groups are assigned their census tract's share noncitizen for matching purposes.] and partisan composition. Each treated census tract is matched to 10 untreated census tract, while each treated block group is treated to 30 untreated block groups. Matching is done with replacement. Tables \ref{tab:blockgroup-table} and \ref{tab:tract-table} present the results of these matches.

>>>>

To test whether neighborhoods with lost voters had systematically lower turnout rates than similar neighborhoods without such disqualifications, I begin by using a matching model. Neighborhoods (defined as census tracts and block groups) are considered treated if they were home to *at least one* lost voter in the 2017 election; they are untreated if no residents were disqualified from the election because of a felony conviction. I use a genetic match to match treated to untreated census tracts and block groups. I match on a series of demographic and political indicators. Estimates of racial characteristics, median income, education, age, population, and share noncitizen^[The Census Bureau does not make noncitizen estimates available at the block group level. As such, block groups are assigned their census tract's share noncitizen for matching purposes.] come from the Census Bureau. Party affiliation rates come from the geocoded voter file. I include voteshare won by the winning city council representative in 2017 as a proxy for the competitiveness of the local race. All else equal, a more competitive race is likely to result in higher turnout.^[Where neighborhoods cross council district lines, this measure is the weighted average of the competitiveness faced by each voter in the neighborhood] These data come from the New York City Board of Elections. Each treated census tract is matched to 10 untreated census tract, while each treated block group is treated to 30 untreated block groups. Matching is done with replacement. Tables \ref{tab:blockgroup-table} and \ref{tab:tract-table} present the results of these matches.
